Robust positively invariant sets for state dependent and scaled disturbances

### 2015-03-23 draft.tex
Made my changes.

\note{We actually do NOT assume that $\Psi$ is invertible! We don't need its inverse at any point! $\Psi^{-1}$ appears only
in this closed form representation but it merely denotes the preimage of $\mathcal X_k$ because that is all we need that the preimages
keep growing. It might be confusing with the notation but that is only
to emphasise that it behaves like the inverse [change notation, e.g.
$\Psi^\dagger$?]}

@@

@@

\note{This looks very MATLAB.. I don't like it [saves space]}

@@

\note{I find the $x^+\approx Ax+Bu$ notation very misleading! I prefer
  $=$ since we will take it as an equality after all not handling
  discretisation errors at all.. [OK - agreed]}

@@

linear feedback  $u=Kx$, where $K$ satisfies the robust Lyapunov condition $V(x)-V((A+BK)x+Dw)\leq \gamma^2w^Tw$ 
with $V(x)=x^T P x\geq0$, i.e. $x^TPx - ((A+BK)x+Dw)^TP((A+BK)x+Dw)\geq x^T(Q+K^TRK)x -\gamma^2 w^Tw$

@@

A representation of disturbances acting on the linearised
model due to linearisation errors can be obtained using the

>>>>

@@

Notice that we do not require $\Psi$ to be invertible, in~\eqref{eq:set:iteration:state:dependent:constraints} $\Psi^{-1}\mathcal X_k$
merely denotes the preimage of $\mathcal X_k$ under the linear map $\Psi$.

@@

@@

@@

linear feedback  $u=Kx$, where $K$ satisfies the robust Lyapunov condition $V(x)-V((A+BK)x+v)\leq \gamma^2v^Tv$ 
with $V(x)=x^T P x\geq0$, i.e. $x^TPx - ((A+BK)x+v)^TP((A+BK)x+v)\geq x^T(Q+K^TRK)x -\gamma^2 v^Tv$

@@

A representation of additive disturbances acting on the linearised
model due to linearisation errors, i.e. a system representation $x^+=Ax + Bu + v$ with an additive disturbance $v$, can be obtained using the
